Ontology Matching with word2vec

### 2016-06-17 Paper/Draft.tex
Wrote blank nodes to Jena

\newpage
\section{Context}
 In this section I will discuss all concepts that are required to understand the study. Firstly, the Semantic Web, the key technology that depends very strongly on Ontology matching, will be discussed. Then the concept of the Ontology itself will be addressed. Lastly, current alignment strategies, their problems and other research and technologies will be discussed.
 \subsection{The Semantic Web}
 The Semantic Web, also called Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide. Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
The Semantic Web, on the other hand, contains sources of \textit{information} that can be combined whenever the user needs it. To stick with the social media example, a person can create a piece of content, say a picture of a tree, and share it with his friends. One of his friends then can share this piece of content with a group of people that likes nature pictures. However, everyone can access all references someone makes. So if a person from the nature group notices the tree is ill and comments on this, the original poster can see this comment and act accordingly. On the current web the friend who shared the picture with the group has to be contacted directly by the commenter and then has to relay the message manually.

@@

 Popular terminological strategies are WordNet comparison and edit distance. The former uses the popular WordNet hierarchy as a distance measure between two concepts, e.g. the number of edges between the concepts and their least general common superconcept\cite{lin2008}.
 Edit distance is a purely string-based similarity measure. The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement. Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities\cite{singh2014, levenshtein}.
 \subsection{Problems in ontology alignment}
 There are a number of different problems ... % Opsommen en samenvatten

@@

 The ternary is to distinguish between blank and non-blank nodes. Blank nodes are a feature of ontologies and thus need to be taken into account.

>>>>

\newpage
\section{Context}
 In this section I will discuss all concepts that are required to understand the study. Firstly, the Semantic Web, the key technology that depends very strongly on Ontology matching, will be discussed. Secondly, the concept of the Ontology itself will be addressed. Thirdly, current alignment strategies and their their problems are discussed. Lastly, other related research and technologies will be discussed. Later sections will refer back to the concepts discussed in this section.
 \subsection{The Semantic Web}
 The first concept is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide. Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
The Semantic Web, on the other hand, contains sources of \textit{information} that can be combined whenever the user needs it. To stick with the social media example, a person can create a piece of content, say a picture of a tree, and share it with his friends. One of his friends then can share this piece of content with a group of people that likes nature pictures. However, everyone can access all references someone makes. So if a person from the nature group notices the tree is ill and comments on this, the original poster can see this comment and act accordingly. On the current web the friend who shared the picture with the group has to be contacted directly by the commenter and then has to relay the message manually.

@@

 Popular terminological strategies are WordNet comparison and edit distance. The former uses the popular WordNet hierarchy as a distance measure between two concepts, e.g. the number of edges between the concepts and their least general common superconcept\cite{lin2008}.
 Edit distance is a purely string-based similarity measure. The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement. Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities\cite{singh2014, levenshtein}.
 \subsection{Problems in ontology alignment}
 There are a number of different problems ... %TODO Opsommen en samenvatten

@@

 The ternary is to distinguish between blank and non-blank nodes. Blank nodes are a feature of ontologies and thus need to be taken into account. Blank nodes can be used to represent concepts with multiple representations, for example a label, a description and a known synonym. More advanced algorithms can take into account all these representations. Another use of a blank node is representing a complex relationship that cannot be represented by an object-predicate-subject triple. For example, if the relationship has a certain confidence or more than two concepts are involved.
